Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-09 writeup/gz_hubble_data.tex
Final proofreading for now, I swear.

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole. The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential. For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms. This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.

The advent of larger telescopes in an increasing range of observable wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.

@@

Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$. These include spheroids and disks (akin to the ellipticals/spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}. Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies. Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology. While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures. Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}. The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.

One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble. The Galaxy Zoo: CANDELS project also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).

@@

\begin{table*}
\center
\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
\hspace{10pt} \emph{GOODS-N~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
\hspace{10pt} \emph{GOODS-N~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
\hspace{10pt} \emph{GOODS-S~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\

@@

By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available. The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel. These images also had the speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH. For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}. This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec and 1.05\arcsec \citep{tan07}.

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.

To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky. This technique was applied only to the coadded Stripe~82 and the COSMOS images.

@@

Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}. This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit. \galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model. All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes. Redshifts used for the SDSS galaxies are all spectroscopic. 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.

\section{Galaxy Zoo interface and classifications}\label{sec:interface}

@@

Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged by not required for participation). Classifications by users not logged in are marked as ``Anonymous''; no weighting is applied to these classifications, but they are otherwise treated identically in the data processing.

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the Galaxy Zoo: Hubble interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
\end{figure*}

@@

The GZH decision tree has four broad sets of morphologies classified by the users. The first option is designating the object as a star or artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked. The second set are smooth galaxies, intended to identify ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies. The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge). The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies. Further annotation for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy. Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and major mergers.

The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image. The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these samples have a median of 46-48~classifications per image (Figure~\ref{fig:classification_hist}).

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/classification_hist.pdf}
\caption{Distribution of the total number of classifications per image for GZH, split by the survey types.}
\label{fig:classification_hist}
\end{figure}

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS, GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the simulated AGN were activated in Dec 2010, as well as a small sample of AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on an overly restrictive cut on blended and/or saturated objects. The main site operated until the launch of the Galaxy~Zoo:~CANDELS project on 10~Sep~2012. Classifications for the GOODS 5-epoch images were obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015. The GZH project had a total of 10,349,357~classifications from 93,898 registered participants. % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift. \citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.

In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample. As a result, the previous methods of correcting for redshift dependent bias will not work. In addition, the effects of band shifting will change the images even more across these redshift ranges. %Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.

In order to test and correct for the effects of redshift, GZH includes a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original \hst{} images.

@@

In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model. This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$). The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.

The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the total sample of redshifted images produced for GZH.

@@

\subsection{Correcting GZH morphologies for classification bias}\label{ssec:zeta}

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user. The combination of all such parameters forms a high-dimensional space, and there are insufficient data to measure their individual effects. Instead, this method uses only two parameters intended to capture the bulk of the change in bias (based on GZ1/GZ2): the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).

@@

\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift. This formula fits the data relatively well (with almost no exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} show examples of the change in vote fraction and their fits to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.

@@

Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is a weak function of galaxy surface brightness. Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts. Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and Poissonian-like variance among the individual voters) means that the average magnitude of $\zeta$ will be less.

@@

\begin{equation}
f_\textrm{features,debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
\label{eqn:fzeta_mod}
\end{equation}

>>>>

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.

@@

The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole. The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's gravitational potential. For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms. This dichotomy has been used to explore much of the astrophysics governing galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.

@@

Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$. These include spheroids and disks (akin to the ellipticals and spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}. Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies. Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology. While these measurements are helped by the fact that the angular diameter distance is relatively flat beyond $z>1$ in a flat $\Lambda$CDM cosmology, the relevant angular scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures. Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the compact sizes of high-redshift galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}. The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.

One of the major difficulties in studying the morphologies of galaxies lies in the techniques used for measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have the advantage of using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble. The Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).

@@

\begin{table*}
\center
\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
\hspace{10pt} \emph{GOODS-N~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
\hspace{10pt} \emph{GOODS-N~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
\hspace{10pt} \emph{GOODS-S~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\

@@

By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available. The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel. These images also had their speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH. For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}. This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.

To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates speckled noise against regions of blank sky. This technique was applied only to the co-added Stripe~82 and the COSMOS images.

@@

Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}. This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit. \galfit{} also provides the parametric \sersic{} index and effective half-light radius for the best-fit model. All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes. Redshifts used for the SDSS galaxies are all spectroscopic. 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the co-add images have a measured DR7 spectroscopic redshift.

\section{GZH interface and classifications}\label{sec:interface}

@@

Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged, but not required for participation). Classifications by users not logged in are marked as ``Anonymous''; no weighting is applied to these classifications, but they are otherwise treated identically in the data processing.

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
\end{figure*}

@@

The GZH decision tree has four broad sets of morphologies classified by the users. The first option is designating the object as a star or image artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked. The second set are smooth galaxies, intended to select ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies. The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge). The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies. Further annotations for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy. Finally, every classification of a galaxy gives users the option of identifying ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and mergers.

The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image. The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these samples have a median of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/classification_hist.pdf}
\caption{Distribution of the total number of classifications per image for GZH, split by survey.}
\label{fig:classification_hist}
\end{figure}

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS, GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the simulated AGN were activated in Dec 2010, as well as a small sample of AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on an overly restrictive cut on blended and/or saturated objects. The main GZH site collected data until its replacement, the Galaxy~Zoo:~CANDELS project, began on 10~Sep~2012. Classifications for the GOODS 5-epoch images were separately obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015. The GZH project had a total of 10,349,357~classifications from 93,898 registered participants. % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie, the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift. \citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.

In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample. As a result, the previous methods of correcting for redshift dependent bias do not work. In addition, the effects of band shifting will change the images even more across these redshift ranges. %Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.

In order to test and correct for the effects of redshift, GZH includes a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$. These images were classified in the GZH interface using the same classification scheme as the original \hst{} images.

@@

In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model. This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$). The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing'' spiral/disc features with increasing redshift for two galaxies with $e=0$.

The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift (since the new images cannot be resampled at better angular resolution than the original SDSS data), as well as the number of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted images produced for GZH.

@@

\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of individual user ability and skill. The combination of all such parameters forms a high-dimensional space, and it is not clear how to separate this into individual effects. Instead, the method used here employs only two parameters intended to capture the bulk of the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).

@@

\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift. This formula fits the data relatively well (with very few exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.

@@

Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is only a weak function of surface brightness ($\mu$). Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts. Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and variance among the individual voters) means that the average magnitude of $\zeta$ will be lower.

@@

\begin{equation}
f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}.
\label{eqn:fzeta_mod}
\end{equation}
